%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Salesforce.com}{Nov 2025 -- Present}
    {Senior Software Engineer (Hyperforce AI)}{Hyderabad}
    \resumeItemListStart
        \resumeItem{ Developed multiple IDE plugins, MCPs, and autonomous Agent Skills as part of the Central DevExp AI Team to automate the end-to-end SDLC, resulting in almost 100\% weekly AI engagement, a 5x reduction in on-call incident analysis time, and a 50\% cut in PR review wait times.}
        \resumeItem{Engineered a provider-agnostic framework by leveraging AI agentic tools to systematically translate and extend 4 core / platform services from native AWS to GCP Tier 1 infrastructure under strict compliance laws.}
    \resumeItemListEnd

    \resumeSubheading
    {Amazon}{Dec 2021 -- Nov 2025}
    {Software Development Engineer 2 (Finance Automation)}{Hyderabad}
    \resumeItemListStart
         \resumeItem{Designed Agentic web automation system using AWS AgentCore processing 15,000+ weekly data extractions across 2,000+ web portals, replacing brittle Selenium scripts and manual workflows. Achieved 92\% accuracy using parallel agents, plan caching and RL, reducing engineering and maintenance support by more than 85\%.}
        \resumeItem{Engineered an LLM-driven Financial Reconciliation Engine processing up to 10M records per day, accelerating anomaly detection and reducing manual work by 65\%. Utilized RAG against historical customer notes and LLM-based semantic mapping to achieve a recon accuracy of 67\%. }
        \resumeItem{Drove VendorHoldbacks re-architecture from monolith to 11 microservices, leading a team of 3 developers, enabling 6M transactions (worth \$2.1B) at 2000 TPS. Transformed batch processing to event-driven architecture, slashing processing time from 24h to near real-time and reducing vendor inquiries by 23.5\% across 14+ countries.}
        \resumeItem{Participated extensively in technical design reviews, providing feedback focused on improving system architecture, scalability, and identifying potential anti-patterns.}
        \resumeItem{Conducted over 1,100 code reviews and championed technical design reviews, providing architecture feedback to enhance scalability, maintainability, and eliminate potential anti-patterns across teams.}
        \resumeItem{Spearheaded roadmap planning and strategic prioritization by advising senior leadership on technical feasibility, engineering complexity, and goal setting for future deliverables.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Amazon}{May 2019 -- Dec 2021}
    {Software Development Engineer 1 (Finance Automation)}{Hyderabad}
    \resumeItemListStart
        \resumeItem{Developed ML-driven automated holdback system preventing \$14.7MM in debit balance exposure. Built scalable pipeline processing 90,000+ vendors' historical data with configurable risk engine using linear regression for seasonal patterns, eliminating manual assessment for 3,600+ high-risk vendors during peak events.}
        \resumeItem{Implemented a data segregation system for special merchants, restricting data access across over 20 input sources and ensuring merchant-specific information security.}
        \resumeItem{Slashed support tickets from 1200+ (2020) to under 20 (2022) through systematic issue resolution. Established robust on-call processes for high-severity incidents, significantly reducing operational load.}
    \resumeItemListEnd

\resumeSubHeadingListEnd