%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Amazon VendorHoldbacks: Re-Architecture} $|$ \emph{Project co-lead}}{}
    \resumeItemListStart
        \resumeItem{Deconstructed a monolithic system into 11 microservices to scale and handle up to 6M transactions worth \$2.1B at up to 2000 TPS from 20+ different sources.}
         \resumeItem{Transformed the batch-based system into an event-driven architecture, reducing payment processing time from 24 hours to near real-time.}
          \resumeItem{Replaced entire SQL-based processing with AWS serverless technologies, improving data accuracy and transparency, reducing annual vendor inquiries by up to 23.5\% across 14+ countries.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Amazon VendorHoldbacks: Rule Engine} $|$ \emph{Project lead}}{}
    \resumeItemListStart
        \resumeItem{Architected a high-performance Rule Engine, evaluating 5000+ concurrent rules with latency of 50ms and processing up to 2000 API calls per second.}
        \resumeItem{Developed a self-service web portal for rule management by business users, reducing rule creation time from 4 weeks of development effort to minutes.}
        \resumeItem{Developed a versatile rule engine that handles any combination of business conditions using the Drools framework.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Amazon VendorHoldbacks: Seasonal Holdbacks} $|$ \emph{Individual}}{}
    \resumeItemListStart
        \resumeItem{Designed automated holdbacks with an interactive seasonality configuration dashboard, streamlining vendor risk management across peak events. (Prime Day, Black Friday, holiday sales, etc.)}
        \resumeItem{Implemented a linear regression ML model to analyze 15+ months of historical vendor behavior, automating risk assessment for 3600+ vendors.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Amazon Approvals: Emails} $|$ \emph{Team Project}}{}
    \resumeItemListStart
        \resumeItem{Built highly configurable email orchestration system handling approval and reminder emails for sending up to 200K approval emails per day.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{IRageCapital: Stock market simulator} $|$ \emph{Individual}}{}
    \resumeItemListStart
        \resumeItem{Developed a high-performance market replay simulator in C++, achieving less than 50 microseconds latency per market execution, enabling backtesting of trading strategies against historical market data.
}
    \resumeItemListEnd

\resumeSubHeadingListEnd